---
output: github_document
---

# Demo module: Calculus in R

This is a demo `{box}`-`{carrier}` module that uses native compiled codes which contains functions involving calculus. 

## Requirements

-  `{carrier}` binary (see [installation](https://joshuamarie.com/carrier/installation.html) for details)
-  Rtools toolchain 
-  `{box}` R package (see [installation](https://joshuamarie.com/carrier/installation.html) for more details)

## Installation

``` bash
carrier install gh:joshuamarie/carrier/tree/main/examples/modules/rcalc --install-deps
```

## Usage

To load the module, use `box::use()`, then you can load the module in few (to several) ways:

```{r}
box::use(
    rcalc, 
    rcalc/spline,            # or rcalc[spline]
    rcalc[quad, brentq],  
)
```

1. First example: Find the root of the function $x^2 - 4$ using Brent's method:

    ```{r}
    rcalc$brentq(\(x) x^2 - 4, 0, 5)
    ```

    Also since you qualify `brentq()`, you can directly use the function:

    ```{r}
    brentq(\(x) x^2 - 4, 0, 5)
    ```

2.  Find the integral of $f(x) = x^2$ from 0 to 5

    ```{r}
    rcalc$quad(\(x) x^2, 0, 5)
    ```
